%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Crypto Quantitative Risk Control Algorithm Research and Development} % Job title
    {Zhejiang University} % Organization
    {Hangzhou, China} % Location
    {Oct. 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a multi-variate fusion risk control algorithm system using agents, incorporating volume-price, sentiment, and on-chain metrics.}
        \item {Built an algorithmic risk control platform in Python, including account risk dashboards and strategy management interfaces.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Quant Research in Cryptocurrency} % Job title
    {Zhejiang University} % Organization
    {Hangzhou, China} % Location
    {Jun. 2025 - Oct. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a primary Solana on-chain trading framework triggered by push signals, achieving long-term sustainable profits.}
        \item {Built a secondary exchange quantitative news trading framework based on LLM agents, achieving 85\% win rate and continuous profitability.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Blockchain R\&D Engineer} % Job title
    {Hangzhou Hyperchain Technology Co., Ltd.} % Organization
    {Hangzhou, China} % Location
    {Oct. 2023 - Jun. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Full-stack learning of blockchain technology and architecture.}
        \item {Conducted thesis and technology report writing on blockchain applications.}
        \item {Performed blockchain industry investment research and market analysis.}
        \item {Contributed to Hyperchain deployment, application development, and product testing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Turing Academy Technology Co., Ltd.} % Organization
    {Remote, China} % Location
    {Jun. 2023 - Sep. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted in AI research projects focused on natural language processing.}
        \item {Applied Python programming with GPT-4 and Claude 2 for research tasks.}
        \item {Contributed to AI model evaluation and optimization.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Analyst Intern} % Job title
    {Zhejiang Youshu Digital Technology Co., Ltd.} % Organization
    {Hangzhou, China} % Location
    {Jan. 2022 - Feb. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted in collecting government-related big data for analysis.}
        \item {Conducted big data analysis for government affairs using statistical methods.}
        \item {Utilized Excel, Python, and other tools for data processing and visualization.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
