%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {Chinese Academy of Sciences Blockchain Association (@opencas\_ucas)} % Organization/group
    {Beijing/Hangzhou, China} % Location
    {Sep. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Engaged in blockchain technology innovation and academic exchange activities.}
        \item {Collaborated on blockchain research projects and academic papers.}
        \item {Participated in technical workshops and seminars on Web3 and blockchain applications.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {Zhejiang University Blockchain Association (@BlockchainZJU)} % Organization/group
    {Hangzhou, China} % Location
    {Oct. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Participated in blockchain-related research and development activities.}
        \item {Organized and conducted technical workshops and seminars on blockchain technology.}
        \item {Contributed to community building and networking within the blockchain ecosystem.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Secretary} % Affiliation/role
    {Association of Employment, Zhejiang Gongshang University} % Organization/group
    {Hangzhou, China} % Location
    {Sep. 2020 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Responsible for assisting the school employment office in organizing large-scale job fairs.}
        \item {Coordinated career development events and workshops for students.}
        \item {Provided support for employment-related activities and initiatives.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Commissary in Charge of Studies} % Affiliation/role
    {Zhejiang Gongshang University} % Organization/group
    {Hangzhou, China} % Location
    {Sep. 2020 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Guided freshmen in Advanced Mathematics and Python Programming.}
        \item {Taught learning skills and study strategies to improve academic performance.}
        \item {Organized study groups and peer tutoring sessions.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
